A Comparison of Graph Processing Systems

### 2020-08-27 documentation/paper/sections/results/results.tex
results for galois speedup sssp

\subsubsection{Single-node}

\autoref{fig:singleNodeSSSP} shows the average calculation times (time without initialization overhead), execution time and the normalized overhead for SSSP on the different frameworks. In these figures, Galois with 96 threads is shown. We show the impact of Galois' thread count in \autoref{sec:galois_speedup}.
\begin{figure*}[t!]
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_calcTime.png}
		\caption{Calculation times for SSSP on a single node}
		\label{fig:singleNodeSSSP_calc}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_execTime.png}
		\caption{Execution times for SSSP on a single node}
		\label{fig:singleNodeSSSP_exec}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_overheadTimeNormalized.png}
		\caption{Overhead time normalized by the graph size in million edges}
		\label{fig:singleNodeSSSP_overheadNormalized}
	\end{subfigure}
	\caption{Average times on a single computation node, black bars represent one standard deviation in our testing.
	The runs on rMat28 for Ligra and Polymer failed and the frameworks were unable to complete the task.}
	\label{fig:singleNodeSSSP}
\end{figure*}

\subsubsection{Distributed}
\begin{figure}[t!]
	\begin{subfigure}{\columnwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedSSSP_calcTime.png}
		\caption{Calculation times for distributed SSSP}
		\label{fig:distributedSSSP_calc}
	\end{subfigure}
	\hfil
	\begin{subfigure}{\columnwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedSSSP_execTime.png}
		\caption{Execution times for distributed SSSP}
		\label{fig:distributedSSSP_exec}
	\end{subfigure}
	\caption{Average times on the distributed cluster, black bars represent one standard deviation in our testing.}
	\label{fig:distributedSSSP}
\end{figure}

@@

\subsection{Galois speedup}
\label{sec:galois_speedup}
For Galois we

\begin{figure}
	\begin{subfigure}{\columnwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSPGaloisThreads.png}
		\caption{Single-source Shortest-paths}
		\label{fig:singleNodeSSSPGaloisThreads}
	\end{subfigure}
	\begin{subfigure}{\columnwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeBFSGaloisThreads.png}
		\caption{Breadth-first search}
		\label{fig:singleNodeBFSGaloisThreads}
	\end{subfigure}
	\caption{Calculation time speedup with increasing thread count for Galois Single-source Shortest-paths and Breadth-first search algorithms.}
\end{figure}

\begin{figure}
	\begin{subfigure}{\columnwidth}
		\includegraphics[width=\columnwidth]{../../plots/singleNodePRPullGaloisThreads.png}
		\caption{PageRank Pull}
		\label{fig:singleNodePRPullGaloisThreads}
	\end{subfigure}
	\begin{subfigure}{\columnwidth}
		\includegraphics[width=\columnwidth]{../../plots/singleNodePRPushGaloisThreads.png}
		\caption{PageRank Push}
		\label{fig:singleNodePRPushGaloisThreads}
	\end{subfigure}
	\caption{Calculation time speedup with increasing thread count for Galois PageRank Push and Pull algorithms.}
\end{figure}

>>>>

\subsubsection{Single-node}
\autoref{fig:singleNodeSSSP} shows the average calculation times (time without initialization overhead), execution time and the normalized overhead for SSSP on the different frameworks. In these figures, Galois with 96 threads is shown. We show the impact of Galois' thread count in \autoref{sec:galois_speedup}.
\begin{figure*}[ht!]
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_calcTime.png}
		\caption{Calculation times for SSSP on a single node}
		\label{fig:singleNodeSSSP_calc}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_execTime.png}
		\caption{Execution times for SSSP on a single node}
		\label{fig:singleNodeSSSP_exec}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_overheadTimeNormalized.png}
		\caption{Overhead time normalized by the graph size in million edges}
		\label{fig:singleNodeSSSP_overheadNormalized}
	\end{subfigure}
	\caption{Average times on a single computation node, black bars represent one standard deviation in our testing.
	The runs on rMat28 for Ligra and Polymer failed and the frameworks were unable to complete the task.}
	\label{fig:singleNodeSSSP}
\end{figure*}

\subsubsection{Distributed}
\begin{figure}
	\begin{subfigure}{\columnwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedSSSP_calcTime.png}
		\caption{Calculation times for distributed SSSP}
		\label{fig:distributedSSSP_calc}
	\end{subfigure}
	\hfil
	\begin{subfigure}{\columnwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedSSSP_execTime.png}
		\caption{Execution times for distributed SSSP}
		\label{fig:distributedSSSP_exec}
	\end{subfigure}
	\caption{Average times on the distributed cluster, black bars represent one standard deviation in our testing.}
	\label{fig:distributedSSSP}
\end{figure}

@@

\subsection{Galois speedup}
\label{sec:galois_speedup}
Analyzing the calculation time speedups for Galois, we can compare how or if the different algorithms benefit from increasing thread numbers.

\subsubsection{Single-source Shortest-path}
\begin{figure}
	\includegraphics[width=\linewidth]{../../plots/singleNodeSSSPGaloisThreads.png}
	\caption{Calculation time speedup with increasing thread count for Galois Single-source Shortest-paths}
	\label{fig:galoisSpeedupSSSP}
\end{figure}
Starting with SSSP which is the algorithm that really is at an advantage when using many threads in \autoref{fig:galoisSpeedupSSSP}.

For all larger graphs, speedup is in most cases very close to optimal up to about 8 threads. 
Twitter has the best speedup, requiring only 38\%\ the calculation time with 2 threads compared to one, 25\%\ using 4 and 12.9\%\ using 8 threads.
Behaviour on friendster is similar with 52\%\ at 2 threads, 29\%\ at 4 and 16\%\ at 8 threads compared to one.

Anything above 32 threads however no longer helps decrease the computation time, in some cases even the opposite e.g. calculation on rMat28 is actually slower with 48 (13\% slower) or 96 threads (28\% slower) compared to 40 threads.

Small graphs like flickr or orkut, neither benefit from more threads nor is the performance held up by synchronization overhead.

\subsubsection{Breadth-first search}
\begin{figure}
	\includegraphics[width=\linewidth]{../../plots/singleNodeBFSGaloisThreads.png}
	\caption{Calculation time speedup with increasing thread count for Galois Breadth-first search}
	\label{fig:galoisSpeedupBFS}
\end{figure}

\begin{figure}
	\begin{subfigure}{\columnwidth}
		\includegraphics[width=\columnwidth]{../../plots/singleNodePRPullGaloisThreads.png}
		\caption{PageRank Pull}
		\label{fig:galoisSpeedupPRPull}
	\end{subfigure}
	\begin{subfigure}{\columnwidth}
		\includegraphics[width=\columnwidth]{../../plots/singleNodePRPushGaloisThreads.png}
		\caption{PageRank Push}
		\label{fig:galoisSpeedupPRPush}
	\end{subfigure}
	\caption{Calculation time speedup with increasing thread count for Galois PageRank Push and Pull algorithms.}
\end{figure}
